Optimizing Large Scale Imaging Surveys for a Retrospective Relative Photometric Calibration

### 2011-12-02 paper/self_calibration_I.tex
euclid: add temporal paragraph
git-svn-id: svn+ssh://astrometry.net/svn/trunk/projects/euclid@19986 03a3cea6-2c03-0410-ac9b-9271b1c66c29

@@

\acknowledgments
\section{Acknowledgments}
We are grateful to

\begin{thebibliography}{}
\bibitem[Padmanabhan et al. (2008)]{pad08} {Padmanabhan, N. et al., An Improved Photometric Calibration of the Sloan Digital Sky Survey Imaging Data, 2008, \apj~674, p1217.}
\bibitem[Windhorst et al. (2011)]{win11}{Windhorst, R.~A. et al., The Hubble Space Telescope Wide Field Camera 3 Early Release Science Data: Panchromatic Faint Object Counts for 0.2-2 $\upmu$m Wavelength, 2011, \apjs~193, p27.}
\bibitem[Wittman et al. (2011)]{wit11}{XX}
\end{thebibliography}
\clearpage

>>>>

As this work was completed in the context of space-based imaging surveys, we have not considered the temporal variation of the relative instrument response as a high priority. We concede that this will have a significant impact on ground-based surveys, where variations on nightly timescales can be expected. The self-calibration procedure discussed in this paper can be trivially modified to fit for a time evolving relative instrument response model. For this to be effective though it will be necessary to not only observe the same sources at very different focal plane positions, but also to observe them at very different times within the survey. To quantify this in more detail, we will include temporal variations in future simulations.

@@

\acknowledgments
\section{Acknowledgments}
DWH was partially supported by NASA (grant XXX), the NSF (grant XXX), and a research fellowship from the Alexander von Humboldt Foundation.

\begin{thebibliography}{}
\bibitem[Padmanabhan et al. (2008)]{pad08} {Padmanabhan, N. et al., An Improved Photometric Calibration of the Sloan Digital Sky Survey Imaging Data, 2008, \apj~674, p1217.}
\bibitem[Windhorst et al. (2011)]{win11}{Windhorst, R.~A. et al., The Hubble Space Telescope Wide Field Camera 3 Early Release Science Data: Panchromatic Faint Object Counts for 0.2-2 $\upmu$m Wavelength, 2011, \apjs~193, p27.}
\bibitem[Wittman et al. (2011)]{wit11}{Wittman, D., Ryan, R. and Thorman, P., Ubercalibration of the Deep Lens Survey, 2011, ArXiv e-prints, 1111.2058}
\end{thebibliography}
\clearpage
